---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Calphad2.5

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/AObaied/Calphad2.5.svg?branch=master)](https://travis-ci.com/AObaied/Calphad2.5)
<!-- badges: end -->

The 2 1/2th Calphad model is capable of extrapolating the Heat capacity (Cp) and Entropy (S) descriptions from the room temperature down to 0 K very accurately, using only two input parameters: The heat capacity and Entropy values at room temperature (Cp298, S298).

## Installation

You can install the released version of Calphad2.5 from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("Calphad2.5")
```

## Example - Pure Si

Temp dependent solution:

```{r example_T_Dep_solution, warning=FALSE}
library(Calphad2.5)

Calculate("Si", CP298 = 20,	S298 = 18.82)
```

## Example - Pure Al

Temp dependent solution:

```{r example_Linear_solution, warning=FALSE}
library(Calphad2.5)

Calculate("Al",  CP298 = 24.209, S298 = 28.275)
```

## Example - Pure Al - Calulate and Plot Heat capacity and Entropy

Temp dependent solution:

```{r example_Linear_solution_plot, warning=FALSE}
library(Calphad2.5)

# Calculate Heat capacity (Cp)
Temp <- seq(1,298.15,1)
Cp <- calculate_Cp(Temp = Temp, compound = "Al",  CP298 = 24.209, S298 = 28.275)

# Plot Heat capacity (Cp)
plot(Temp,Cp,type="line", lwd=2, xlab = "Temperature, K", ylab = "Cp, J/(mol.K)")
points(298.15, 24.209)

# Calculate Entropy (S)
S <- calculate_S(Temp = Temp, compound = "Al",  CP298 = 24.209, S298 = 28.275)

# Plot Entropy (S)
plot(Temp,S,type="line", lwd=2, xlab = "Temperature, K", ylab = "S, J/(mol.K)")
points(298.15, 28.275)

```

## Example - Pure Si - Calulate and Plot Heat capacity and Entropy

Temp dependent solution:

```{r example_T_Dep_solution_plot, warning=FALSE}
library(Calphad2.5)

# Calculate Heat capacity (Cp)
Temp <- seq(1,298.15,1)
Cp <- calculate_Cp(Temp = Temp, compound = "Si", CP298 = 20, S298 = 18.82)

# Plot Heat capacity (Cp)
plot(Temp,Cp,type="line", lwd=2, xlab = "Temperature, K", ylab = "Cp, J/(mol.K)")
points(298.15, 20)

# Calculate Entropy (S)
S <- calculate_S(Temp = Temp, compound = "Si", CP298 = 20, S298 = 18.82)

# Plot Entropy (S)
plot(Temp,S,type="line", lwd=2, xlab = "Temperature, K", ylab = "S, J/(mol.K)")
points(298.15, 18.82)
```
